---
title: "Codebook.rmd"
author: "Daniel Clark & Grace Lang"
date: "6/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(readxl)
```

## Anheiser Busch Brewery Descriptive Statistical Analysis

This codebook provides an overview of the data as it was received and any modifications that were required to support our analysis. It is a documentation of the variables in the data set, any normalization or modifications that were made, and should support replication of our analysis. 

### Data Files Received

DDSAnalytics provided our consulting group with a Comma Delimited File (.csv) file titled Beers.csv & Breweries.csv. 

```{r data import}
BeersCSV <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Beers.csv"
Beers <- read.csv(url(BeersCSV))

BrewCSV <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Breweries.csv"
Brew <- read.csv(url(BrewCSV))

```

### Initial Data Structure

The data contained within the provided table has the following variable names and types: 
<br>

```{r}
kable(t(lapply(Beers,class)))%>%
  kable_styling()%>%
  scroll_box(height = 100, width = 500)
```

Derived variables include: 

# Beers.csv

| Variable              | Values        | Purpose                                                |
|-----------------------|:-------------:|-------------------------------------------------------:|
| Name         | factor        | Name of individual beer |
| Beer_ID          | integer        | Unique identifier for the individual beer   |
| ABV              | numeric       | Alcohol by volume of the beer       |
| IBU            | integer       | International Bitterness Units of the beer     |
| Brewey_ID               | integer       | Brewery ID associated with the individual beer                  |
| Style           | factor       | Style of the beer             |
| Ounces | numeric    | Ounces of beer   | 

# Breweries.csv

| Variable              | Values        | Purpose                                                |
|-----------------------|:-------------:|-------------------------------------------------------:|
| Brew_ID        | integer        | Unique identifier of the brewery |
| Name          | factor        | Name of the brewery  |
| City             | factor       | City where the brewery is located       |
| State            | factor       | U.S. State where the brewery is located     |

### Test Models

A number of test models were created to help identify features provided in the data set that contribute to Attrition rates within the population. 

#### Model 1: Logistic Regression

A logistic regression model to predict whether an employee -- based on provided features -- would be in class (AttritionCode = 1) or out of Class. This model accepts all of the provided categorical and continuous variables and determines their impact on Attrition. The model is un-normalized and unweighted and provides only a first step analysis. Despite this, however, it is capable of achieving accuracy rates of 87% with Precision values of 90.7% and Recall of 94.9%. 

This model is described by the statement: 

```{r eval=FALSE, echo=TRUE}
AttritionCode ~ Age + JobRole + StockOptionLevel + WorkLifeBalance + 
              YearsSinceLastPromotion + EnvironmentSatisfaction + JobInvolvement + 
              OverTime + RelationshipSatisfaction + YearsAtCompany + YearsWithCurrManager + 
              BusinessTravel + DistanceFromHome + Gender + MaritalStatus + 
              NumCompaniesWorked + YearsInCurrentRole
```
