---
title: "Codebook.rmd"
author: "Daniel Clark & Grace Lang"
date: "6/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(readxl)
```

## Anheiser Busch Brewery Descriptive Statistical Analysis

This codebook provides an overview of the data as it was received and any modifications that were required to support our analysis. It is a documentation of the variables in the data set, any normalization or modifications that were made, and should support replication of our analysis. 

### Data Files Received

Anheiser Busch provided our consulting group with two Comma Delimited files (.csv) file titled Beers.csv & Breweries.csv. 

```{r data import}
BeersCSV <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Beers.csv"
Beers <- read.csv(url(BeersCSV))

BrewCSV <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Breweries.csv"
Brew <- read.csv(url(BrewCSV))

```

### Data Collection

It is unclear how this data was collected. Our consulting group contacted the source, but did not receive a description on the methodology used. Because of this unknown, when there was incomplete data, our consulting group dropped the rows used in final analysis. 

### Initial Data Structure

The data contained within the provided table has the following variable names and types: 
<br>


Derived variables include: 

### Beers.csv

```{r}
kable(t(lapply(Beers,class)))%>%
  kable_styling()%>%
  scroll_box(height = 100, width = 500)
```



| Variable              | Values        | Purpose                                                |
|-----------------------|:-------------:|-------------------------------------------------------:|
| Name         | factor        | Name of individual beer |
| Beer_ID          | integer        | Unique identifier for the individual beer   |
| ABV              | numeric       | Alcohol by volume of the beer       |
| IBU            | integer       | International Bitterness Units of the beer     |
| Brewey_ID               | integer       | Brewery ID associated with the individual beer                  |
| Style           | factor       | Style of the beer             |
| Ounces | numeric    | Ounces of beer   | 


### Breweries.csv

```{r}
kable(t(lapply(Brew,class)))%>%
  kable_styling()%>%
  scroll_box(height = 100, width = 500)
```



| Variable              | Values        | Purpose                                                |
|-----------------------|:-------------:|-------------------------------------------------------:|
| Brew_ID        | integer        | Unique identifier of the brewery |
| Name          | factor        | Name of the brewery  |
| City             | factor       | City where the brewery is located       |
| State            | factor       | U.S. State where the brewery is located     |

### Data Cleaning

The two tables can be joined on Beers.Brewery_ID and Breweries.Brew_ID. There are a handful of breweries that have duplicate name and different Brewery ID. They can be identified and resolved with the following code. 

```{r}
Brew$Name[duplicated(Brew$Name)]
#checking our dataframe, we can identify some duplicates in our dataset. Let's investigate further to see if any need to be removed.
Brew[Brew$Name=='Blackrocks Brewery',] # appears that flying sailor is a part of the MI blackrocks, so combine them
Brew[Brew$Name=='Summit Brewing Company',] # both appear to be the same brewery, so combine 159 into 39
Brew[Brew$Name=='Otter Creek Brewing',] # looks like middlebury is the correct location
Brew[Brew$Name=='Sly Fox Brewing Company',] # this appears to be two actual locations of the same brewery, so let's leave as is, same state
Brew[Brew$Name=='Blue Mountain Brewery',] #appears to be two locations of the same brewery. Keep as is for now, same state
Brew[Brew$Name=='Lucette Brewing Company',] # looks like the correct spelling of the city is Monomonie, so we'll need to change the other
Brew[Brew$Name=='Oskar Blues Brewery',] #looks like the correct location is longmont


#Combining two tables 
colnames(Beers)[colnames(Beers)=="Brewery_id"] <- "Brew_ID" #Rename for the same key
Combined <- merge(Beers, Brew, by = "Brew_ID") # Merge files
colnames(Combined)[colnames(Combined)=="Name.x"] <- "Beer Name"
colnames(Combined)[colnames(Combined)=="Name.y"] <- "Brewery_Name"


#Combining the duplicate Breweries into one Brew_ID and fixing some data entry issues, proved by Google searches

Combined[Combined$Brew_ID == '96',"Brew_ID"] <- 13
Combined$State <- as.character(Combined$State) #refactoring the whole column, so insert should work
Combined[Combined$Beer_ID == 2449 ,"State"] <- "MI" ## needs work, throwing error 'invalid factor level, NA generated'
Combined[Combined$Brew_ID == '139',"Brew_ID"] <- 59
Combined[Combined$Beer_ID == 2352 ,"City"] <- "St. Paul"
Combined[Combined$Brew_ID == '262',"Brew_ID"] <- 276
Combined[Combined$Brew_ID == 276 ,"City"] <- "Middlebury"
Combined[Combined$Brew_ID == '378',"Brew_ID"] <- 457
Combined$City <- as.character(Combined$City) #refactoring the whole column, so insert should work
Combined[Combined$Beer_ID == 1571 ,"City"] <- "Menomonie"
Combined[Combined$Brew_ID == '504',"Brew_ID"] <- 167
Combined[Combined$Brew_ID == 167 ,"City"] <- "Longmont" 

```

