---
title: "Assignment09_Summer19_Grace_Lang"
author: "Grace Lang"
date: "7/7/2019"
output:
  pdf_document: default
  html_document: default
---

# A) Clean and Prepare the data:
```{r setup}

library(dplyr)
library(tidyverse)
library(ggplot2)
library(stats)
library(caret)
library(rmarkdown)
library(tinytex)

#Loading the two files
BeersCSV <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Beers.csv"
Beers <- read.csv(url(BeersCSV))

BrewCSV <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Breweries.csv"
Brew <- read.csv(url(BrewCSV))

#Merging the two files
colnames(Beers)[colnames(Beers)=="Brewery_id"] <- "Brew_ID" #Rename for the same key
Combined <- merge(Beers, Brew, by = "Brew_ID") # Merge files
colnames(Combined)[colnames(Combined)=="Name.x"] <- "Beer Name"
colnames(Combined)[colnames(Combined)=="Name.y"] <- "Brewery_Name"

##Check to see where spaces fall
#head(paste(Combined$State),5)

#Create a function for trimming states
trim <- function(x) { gsub("(^[[:space:]]+|[[:space:]]+$)", "", x) }
Combined_Trimmed <- Combined[,1:9]
Trimmed_State <- data.frame(State = trim(Combined$State))
Combined <- cbind(Combined_Trimmed,Trimmed_State)

##Check to ensure spaces are gone
#head(paste(Combined$State),5)


#One dataset with no IBU/NAs and only filter on TX & CO
beerCOTX <- Combined %>% subset.data.frame(State == c("CO","TX")) %>% arrange(IBU) %>% na.omit()

```

# B) Create an initial plot of the data
```{r plot}
#Plot 
ggplot(beerCOTX, aes(x=IBU, y=ABV)) +
    geom_point(shape=1) +    # Use hollow circles
    facet_grid(rows= vars(State)) +
    theme_grey() +
    theme(plot.title = element_text(hjust=0.5)) + labs(x="IBU", y="ABV", title = "IBU vs ABV") 

```

# C) Model the data
```{r model}
#Plot regression line for each state
beerCO <- subset.data.frame(beerCOTX, State == "CO")
beerTX <- subset.data.frame(beerCOTX, State == "TX")

regCO <- lm(ABV~IBU, data = beerCO)
plot(ABV~IBU, data =beerCO, main = "Colorado IBU vs ABV", xlab= 'ABV', ylab = 'IBU') + abline(regCO, col="blue")

regTX <- lm(ABV~IBU, data = beerTX)
plot(ABV~IBU, data =beerTX, main = "Texas IBU vs ABV", xlab= 'ABV', ylab = 'IBU') + abline(regTX, col="blue")

#Faceted GGPlot for reference
#ggplot(beerCOTX, aes(x=IBU, y=ABV)) +
#    geom_point(shape=1) +    # Use hollow circles
#    geom_smooth(method = "lm") + 
#    facet_grid(rows= vars(State)) +
#    theme_grey() +
#    theme(plot.title = element_text(hjust=0.5)) + labs(x="IBU", y="ABV", title = "IBU vs ABV") 

```
## Assumptions of the regression model:
### 1. There is a normal distribution of the ABV for fixed values of IBU
No, the data is right skewed for both TX & CO
### 2. These normal distributions have equal standard deviations. 
No based on the residual graph, the residuals do not have a consistent variance or standard dev
### 3. The means of these normal distributions have a linear relationship with IBU.  
### 4. Independence (you may assume this one to be true without defense.)   


# D) Gain inference from the model
```{r parameter}
summary(regCO)
summary(regTX)

#Each individual residuals for data
#regCO$resid
#regTX$resid

#Are the residuals normal
histogram(regCO$resid)
histogram(regTX$resid)
#Do the residuals have a constant variance
ggplot(regCO, aes(x=.fitted,y=.resid)) +geom_point() + geom_line(aes(y=0))
ggplot(regTX, aes(x=.fitted,y=.resid)) +geom_point() + geom_line(aes(y=0))
par(mfrow = c(2,1))
plot(regCO, which=1:2)
plot(regTX, which=1:2)
#The residuals look like a random cloud; however, they do not seem to have a constant variance.


```
## Interpret the Slope

## Is there evidence that the relationship between ABV and IBU is significantly different for Texas and Colorado beers?  
### Both Texas and Colorado have right-skewed distributions; however, Colorado is less right-skewed than Texas

# E) Compare two competing models: External Cross Validation
```{r cross}
beerCOTX_log = beerCOTX %>% mutate(IBU2 = IBU^2)
head(beerCOTX_log,5)

beerCO_2 <- subset.data.frame(beerCOTX_log, State == "CO")
beerTX_2 <- subset.data.frame(beerCOTX_log, State == "TX")

#Training datasets
set.seed(1)

TrainCO = sample(seq(1,dim(beerCO_2)[1]),round(.60*dim(beerCO_2)[1]),replace = FALSE)
CO_Train = beerCO_2[TrainCO,]
CO_Train
CO_Test = beerCO_2[-TrainCO,]
CO_Test

TrainTX = sample(seq(1,dim(beerTX_2)[1]),round(.60*dim(beerTX_2)[1]),replace = FALSE)
TX_Train = beerTX_2[TrainTX,]
TX_Train
TX_Test = beerTX_2[-TrainTX,]
TX_Test


#CO linear
CO_1_fit = lm(ABV~IBU, data = CO_Train)
summary(CO_1_fit)
CO_1_Preds = predict(CO_1_fit, newdata = CO_Test)
as.data.frame(CO_1_Preds)
error <- CO_1_Preds - CO_Test$IBU
square_error <- error^2
ASE <- mean(square_error)
ASE
#2286.503

#TX linear
TX_1_fit = lm(ABV~IBU, data = TX_Train)
summary(TX_1_fit)
TX_1_Preds = predict(TX_1_fit, newdata = TX_Test)
as.data.frame(TX_1_Preds)
error <- TX_1_Preds - TX_Test$IBU
square_error <- error^2
ASE <- mean(square_error)
ASE
#1879.79

#CO log
CO_2_fit = lm(ABV~IBU2, data = CO_Train)
summary(CO_2_fit)
CO_2_Preds = predict(CO_2_fit, newdata = CO_Test)
as.data.frame(CO_2_Preds)
error <- CO_2_Preds - CO_Test$IBU2
square_error <- error^2
ASE <- mean(square_error)
ASE
#12817275

#TX log
TX_2_fit = lm(ABV~IBU2, data = TX_Train)
summary(TX_2_fit)
TX_2_Preds = predict(TX_2_fit, newdata = TX_Test)
as.data.frame(TX_2_Preds)
error <- TX_2_Preds - TX_Test$IBU2
square_error <- error^2
ASE <- mean(square_error)
ASE
#7005430

<<<<<<< HEAD
```
=======
```    
>>>>>>> 097c101c700361a80ee39639293e0729c30bec72
