---
title: "Case_Study_02_Grace_Lang"
author: "Grace Lang"
date: "8/1/2019"
output: html_document
---
# Data Setup
Read in the data
```{r setup, include=FALSE}
library(ggplot2)
library(fpp)
library(fpp2)
library(dygraphs)
library(statsr)
library(mltools)
library(caret)

url <- "https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/UNIT%2014/CaseStudy2-data.csv"

Initial <- read.csv(url, header=TRUE, sep=",")
```

Explore the structure of the data
```{r structure}
str(Initial)
summary(Initial)
```

Drop columns that wont add value to analysis:    
  * ID = row number    
  * EmployeeCount = 1    
  * Over18 = Y    
  * StandardHours = 80    
```{r drop}
Initial$ID <- NULL
Initial$EmployeeCount <- NULL
Initial$Over18 <- NULL
Initial$StandardHours <- NULL
```

Create a couple custom variables:
```{r column create}
Initial$Education <- as.factor(Initial$Education)
Initial$EducationLevel <- interaction(Initial$EducationField, Initial$Education)

Initial$JobLevel <- as.factor(Initial$JobLevel)
Initial$JobRoleLevel <- interaction(Initial$JobRole, Initial$JobLevel)

```

Descriptive Statistics
```{r}
cbbPalette <- c("#E69F00", "#009E73")

ggplot(Initial, aes(Attrition,fill=Attrition)) + geom_bar(fill = cbbPalette ) + theme_minimal() + theme(plot.title = element_text(hjust=0.5), legend.position ="none") + labs(x="Did Employee Leave Company?", y="Number of Employees", title = "Number of Employees Who Left Frito Lay") 

prop.table(table(Initial$Attrition))

#Employees who live closer to workhave a higher attrition rate
ggplot(Initial, aes(DistanceFromHome,fill=Attrition)) + geom_bar() + theme_minimal() + theme(plot.title = element_text(hjust=0.5)) + labs(x="Distance From Home", y="Number of Employees") 

#As job level increases the amount of people who leave decreases
ggplot(Initial, aes(JobLevel,fill=Attrition)) + geom_bar() + theme_minimal() + theme(plot.title = element_text(hjust=0.5)) + labs(x="Job Level", y="Number of Employees") 

#There are higher rates of attrition with lower job satisfaction
ggplot(Initial, aes(JobSatisfaction,fill=Attrition)) + geom_bar() + theme_minimal() + theme(plot.title = element_text(hjust=0.5)) + labs(x="Job Satisfaction", y="Number of Employees") 
```


# Training & Test Set
```{r training}
set.seed(7)
Set = sample(seq(1,dim(Initial)[1]),round(.60*dim(Initial)[1]),replace = FALSE)
#Training Set
Train = Initial[Set,]
#Test Set
Test = Initial[-Set,]

#Check to see if it pulled 60/40% 
#dim(Test) 348  32
#dim(Train) 522  32

```

# KNN Model
The accuracy for this model is around 84%; however, it does not meet the 60/60 sensitivity/specificity requirement. 
```{r knn}
set.seed(7)
fit_knn <- train(Attrition~.,Train,method = 'knn',trControl = trainControl(method = 'repeatedcv',number = 3))
Predict_knn <- predict(fit_knn,Test)

confusionMatrix(Test$Attrition, Predict_knn)

```

# Other Models for reference
The Support Vector Machine (SVM) has the highest accuracy without sacrificing the sensitivity and specificity results. 
```{r other}
library(mboost)
library(kernlab)
library(randomForest)

set.seed(7)
#fit_nn <- train(Attrition ~.,Train,method = 'pcaNNet',trControl = trainControl(method = 'repeatedcv',number = 3),tuneGrid = expand.grid(size = 25,decay = 0.01))

#fit_glmBoost <- train(Attrition~.,Train,method = 'glmboost',trControl = trainControl(method = 'repeatedcv',number = 3))
fit_rf <- train(Attrition ~.,Train,method = 'rf', trControl = trainControl(method = 'repeatedcv',number = 3)) 
fit_glm <- train(Attrition~.,Train,method = 'glm',trControl = trainControl(method = 'repeatedcv',number = 3))
fit_svm <- train(Attrition~.,Train,method = 'svmRadial',trControl = trainControl(method = 'repeatedcv',number = 3))



Predictions_rf <- predict(fit_rf, Test)
Predictions_glm <- predict(fit_glm, Test)
Predictions_svm <- predict(fit_svm,Test)


confusionMatrix(Test$Attrition, Predictions_rf) #89% accuracy, 89/94% Sens/Spec
confusionMatrix(Test$Attrition, Predictions_glm) #89% accuracy, 94/63% Sens/Spec
confusionMatrix(Test$Attrition, Predictions_svm) #88% accuracy, 88/100% Sens/Spec
```


# Logistic Regression Model
```{r regression}
set.seed(7)
model <- glm(Attrition ~ Age+BusinessTravel+Department+DistanceFromHome+
               Education+EducationField+EnvironmentSatisfaction+Gender+JobInvolvement+
               JobLevel+JobRole+JobSatisfaction+MaritalStatus+MonthlyIncome+NumCompaniesWorked+
               OverTime+PercentSalaryHike+PerformanceRating+RelationshipSatisfaction+
               TotalWorkingYears+TrainingTimesLastYear+WorkLifeBalance+ 
               YearsAtCompany+YearsInCurrentRole+YearsSinceLastPromotion+
               YearsWithCurrManager,family=binomial(link='logit'),data=Train)

summary(model)
```

# CART Model
```{r decision tree}
fit_rpart <- train(Attrition ~.,Train,method = 'rpart', trControl = trainControl(method = 'cv',number = 3))
Predictions_rpart <- predict(fit_rpart,Test)
confusionMatrix(Test$Attrition, Predictions_rpart)

```

